P4Query: Static Analyser Framework for P4

### 2021-03-26 publications/The_tool_intro/paper.tex
too_intro: some minor changes

	\begin{abstract}
		There are many important tasks in a conventional software development process which can be supported by different analysis techniques. P4 is a high level domain specific language for
describing the data plane layer of packet processing algorithms. It has several uncommon language elements and concepts often make analysis of P4 programs a laborious task. 
The paper presents P4Query, a generic analysis framework for P4 makes possible development of different P4 related analysis methods in a generic and modular way. The framework uses an integral graph representation which contains the results of applied analysis methods too. This way the framework supports rapid implementation of new analysis methods in a way where the results will be also easily reusable by other methods.

@@

	Comparing these approaches this paper presents a generic framework make possible to implement several analyses methods which can use each other's results as well.

  A major inspiration for this work was RefactorErl~\cite{referl}, a static analysis tool for Erlang. RefactorErl stores program information in a graph called the Semantic Program Graph using relation databases, and hosts in own query language for exploring the stored information. Many features in our work -- such as using graph databases and their built-in query languages instead of in-house solutions -- can be considered to be the streamlining of best practices found in RefactorErl.

@@

  The expressive power of Gremlin is proved in another recent work~\cite{yamaguchi}: the authors store C code information in Neo4j, and define recurring vulnerability patterns as Gremlin queries. Using this approach, the authors discovered 18 previously unknown vulnerabilities in the Linux kernel.

@@

P4 is a relatively new, domain specific language having some uncommon language elements (for example match-action tables). The language makes possible the description of the data plane layer of packet processing algorithms. However for a real execution also a corresponding control plane layer is needed, which part is more or less a black hole while we consider only the P4 source code. Because of these testing, verification and generally functional and non-functional analysis of P4 programs are non trivial tasks sometimes requiring language specific techniques.

@@

This paper presents a framework allows the implementation of different analysis methods using a common basis. The framework applies an extensible integral graph representation where the results of the different analysis methods are represented also as part of the graph. This makes possible execution of different methods in a hierarchical order where methods can use the results (or some part of the results) of previously applied methods.

>>>>

	\begin{abstract}
		There are many important tasks in a conventional software development process which can be supported by different analysis techniques. P4 is a high level domain specific language for
describing the data plane layer of packet processing algorithms. It has several uncommon language elements and concepts often make analysis of P4 programs a laborious task. 
The paper presents P4Query, a generic analysis framework for P4 makes possible development of different P4 related analysis methods in a generic and modular way. The framework uses an internal graph representation which contains the abstract syntax tree of the analysed program and the results of applied analysis methods too. The framework supports rapid implementation of new analysis methods in a way where the results will be also easily reusable by other methods.

@@

	Comparing these approaches this paper presents a generic framework make possible to implement several analyses methods using a common basis. A major inspiration for this work was RefactorErl~\cite{referl}, a static analysis tool for Erlang. RefactorErl stores program information in a graph called the Semantic Program Graph using relation databases, and hosts in own query language for exploring the stored information. Many features in our work -- such as using graph databases and their built-in query languages instead of in-house solutions -- can be considered to be the streamlining of best practices found in RefactorErl.

@@

  For the manipulation of the internal graph representation we use the Gremlin language. The expressive power of Gremlin is proved in another recent work~\cite{yamaguchi}: the authors store C code information in Neo4j, and define recurring vulnerability patterns as Gremlin queries. Using this approach, the authors discovered 18 previously unknown vulnerabilities in the Linux kernel.

@@

P4 is a relatively new, domain specific language having some uncommon language elements (for example match-action tables). The language makes possible the description of the data plane layer of packet processing algorithms. However for a real execution also a corresponding control plane layer is needed, which part is more or less a black hole while we consider only the P4 source code. Because of these testing, verification and generally functional and non-functional analysis of P4 programs are non trivial tasks which sometimes require language specific techniques.

@@

This paper presents a framework allows the implementation of different analysis methods using a common basis. The framework applies an extensible internal graph representation where the results of the different analysis methods are represented also as part of the graph. This makes possible execution of different methods in a hierarchical order where methods can use the results (or some part of the results) of previously applied methods.
